---
title: "Segmentation Project"
author: "Nissa Febriani"
date: "5/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Library Preparation
```{r}
library(tidyverse) 
library(cluster) 
library(factoextra)
library(ggplot2)
```


Reading the Data
```{r}
setwd("C:/Users/Dell/Downloads/WDR")
getwd

movie <- read.csv("customer_movie_rating.csv")
movie2 <- read.csv("customer_movie_rating.csv")

```


Summary of the data
```{r}
head(movie)
```

```{r}
glimpse(movie)
```
The dataset consists of 291 data regarding the assessment of 5 film genres, namely horror, romcom, action, comedy, and fantasy. 


Cleaning the Data
```{r}

movie <- na.omit(movie)
movie <- scale(movie)

head(movie)
```


Choosing k-optimal
```{r}
set.seed(123)
fviz_nbclust(movie, kmeans, method = "wss")
```
```{r}
set.seed(123)
fviz_nbclust(movie, kmeans, method ="silhouette")
```
```{r}
library(cluster)
# compute gap statistic
set.seed(123)
gap_stat <- clusGap(movie, FUN = kmeans, nstart = 25, K.max = 10, B = 50)


# Print the result
print(gap_stat, method = "firstmax")
fviz_gap_stat(gap_stat)
```

Based on the optimal search for k, k = 3 will be selected 


Building K-means Model
```{r}
k3 <- kmeans(movie, centers = 3, nstart = 25)

str(k3)
```

Visualizing the Model
```{r}
fviz_cluster(k3, data = movie)
```
```{r}
head(movie2)
```



Cluster Analysis
```{r}
str(k3)

movie2 %>%
  mutate(Cluster = k3$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")
```

```{r}

movie %>%
  as_tibble() %>%
  mutate(cluster = k3$cluster, score = row.names(movie)) %>%
  ggplot(aes(Horror, Comedy, color = factor(cluster), label = score)) + geom_text()


```
Explanation:
Cluster 1 is a group that gives high marks to the comedy genre and low scores to the horror genre. Cluster 2 is a group that gives high marks to the comedy genre and gives moderate ratings to the horror genre.
Cluster 3 is a group that gives low marks to the comedy genre and gives high marks to the horror genre.






